The impact of gas bulk rotation on the Lyman-$\alpha$ line

### 2013-10-21 paper/ms.tex
Fig 10 fixed bugs

\altaffiltext{1}{Departamento de F\'{i}sica, Universidad de los Andes, Cra. 1
No. 18A-10, Edificio Ip, Bogot\'a, Colombia}
\altaffiltext{2}{--}

\begin{abstract}
We present novel results of radiative transfer calculations to measure
the impact of gas bulk rotation on the morphology of the Lyman
$\alpha$ line in galaxies. We model a galaxy as a sphere with an
homogeneous mixture of dust and hydrogen at a constant
temperature. These spheres have a solid-body rotation with
maximum velocities in the range $0-300$ \kms. The neutral
hydrogen optical depths are in the range $\tau_{\rm
H}=10^{5}-10^{7}$. We also consider two kinds of spatial
distribution for the radiation sources with respect to the sphere:
central and homogeneous. We find that the line width and the amount of
Lyman alpha photons escaping in the line center increase with
rotational velocity. higher rotational velocities increase the width
of each peak in the outgoing line profile while it also increases the
amount of Lyman alpha photons escaping in the line. For large
rotational velocities and high Hydrogen optical depths the outgoing
line presents single peak a the line center. This trend is more
pronounced for radiation sources homogeneously distributed in the
sphere. Rotation increases by a factor of $2$ the escape fraction for
systems with homogeneously distributed sources. For radiation sources
located off-center, the line morphology presents a range of single,
double and triple peak lines. This work demonstrates that gas bulk
rotation has a non negligible impact on the morphology of the Lyman
$\alpha$ line.

@@

We start by a quantitative discussion of the line morphology. Here we
follow a classification of $Ly\alpha$ profiles made by
\cite{Kulas12}. They presented observational results for star forming
galaxies at $z=2$-$3$ that showed multiple peaks in their emission.
They classified the observed lines into four groups. In Group I the
red peak is stronger than the blue, For our porpoises Group II and Group II
with the blue peak stronger are the same, Group IV contains double-peak
profiles with roughly the same flux and finally group IV present multi-peaked 
lines.

>>>>

\altaffiltext{1}{Departamento de F\'{i}sica, Universidad de los Andes, Cra. 1
No. 18A-10, Edificio Ip, Bogot\'a, Colombia}
\altaffiltext{2}{Max Planck Institute for Astrophysics, Karl-Schwarzschild-Str. 1, 85741, Garching, Germany}

\begin{abstract}
We present novel results of radiative transfer calculations to measure
the impact of gas bulk rotation on the morphology of the Lyman
$\alpha$ line in galaxies. We model a galaxy as a sphere with an
homogeneous mixture of dust and hydrogen at a constant
temperature. These spheres have a solid-body rotation with
maximum velocities in the range $0-300$ \kms and neutral
hydrogen optical depths in the range $\tau_{\rm
H}=10^{5}-10^{7}$. We also consider two kinds of spatial
distribution for the radiation sources with respect to the sphere:
central and homogeneous. We find that the line width and the amount of
Lyman $\alpha$ photons escaping in the line center increase with
the rotational velocity. For large
rotational velocities and high Hydrogen optical depths the outgoing
line presents single peak a the line center. This trend is more
pronounced for radiation sources homogeneously distributed in the
sphere. Rotation also increases by a factor of $2$ the escape fraction for
systems with homogeneously distributed sources. For radiation sources
located off-center, the line morphology presents a range of single,
double and triple peaked lines. This work demonstrates that gas bulk
rotation has a non negligible impact on the morphology of the Lyman
$\alpha$ line.

@@

We start by a quantitative discussion of the line morphology. Here we
follow a classification of $Ly\alpha$ profiles made by
\cite{Kulas12}. They presented observational results for star forming
galaxies at $z=2$-$3$ that showed multiple peaks in their emission.
They classified the observed lines into four groups. In Group I the
red peak is stronger than the blue, in Group II the blue peak is
stronger, in Group III the two peaks have the same strength and Group
IV LAEs present multiple peaks.
